### 2023-04-16 main.tex
ii
ll
z

In this work we concentrate our effort in this last "single layer" case with a repulsive process, i.e. a dynamic in which a maximum amount of particles can be present in each site at each time. We will call this amount, the "maximal occupancy" and it will indicated with $\twoj$ where $\twoj\in\mathbb{N}$. Particle of any species can exchange their position in the graph, under this exclusion constraint. The system will be put out of equilibrium and some absorbing duality result are investigated. Moreover, we will use this duality, to study the out of equilibrium steady state. In particular, in case of $\twoj=1$ we retrieve the model studied in \cite{vanicat2017exact}. We will then exploit this last result and the duality, to write explicitly all the correlations of this \textit{hard-core exclusion} case. The main tool that we will use is the Lie algebraic description of the process, that allows to find the duality as a proper symmetry of the generator. 

@@

    &\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}

@@

    \sum_{c=2}^{N}(E_{c1}^{x})\right)\\&+\alpha_{1}^{x}\sum_{b=2}^{N}\left(E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)+\sum_{a=2}^{N}\sum_{b=2}^{N}\alpha_{a}^{x}\left(E_{ba}^{x}+E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)
    \\&=\sum_{a=2}^{N}\alpha_{a}^{x}E_{1a}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{b=2}^{N}E_{bb}^{x}=

@@

@@

@@

        \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}\beta_{s_{3}}+\frac{(L-y_{1})}{(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}\beta_{s_{3}}

@@

        \frac{(L-y_{2})}{(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\beta_{s_{3}}+\frac{(L-y_{3})}{(L+1)}(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}\beta_{s_{2}}

@@

>>>>

In this work we concentrate our effort in this last "single layer" case with a repulsive process, i.e. a dynamic in which a maximum amount of particles can be present in each site at each time. We will call this amount, the "maximal occupancy" and it will indicated with $\twoj$ where $\twoj\in\mathbb{N}$. Particle of any species can exchange their position in the graph, under this exclusion constraint. The system will be put out of equilibrium and some absorbing duality result are investigated. Moreover, we will use this duality, to study the out of equilibrium steady state. In particular, in case of $\twoj=1$ we retrieve the model studied in \cite{vanicat2017exact}. 
The case of $\twoj=1$ distinguishes itself from other values of $\twoj$ as in this case the model can be mapped to an integrable higher rank $gl(n)$ Heisenberg XXX spin chain with open (non-diagonal) boundaries. Furthermore the matrix product ansatz \cite{derrida1993exact}  is applicable, see \cite{Crampe:2014aoa,vanicat2017exact}.
We will exploit   the duality and th underlying symmetries of the model, to write explicitly all the correlations of this \textit{hard-core exclusion} case. The main tool that we will use is the Lie algebraic description of the process, that allows to find the duality as a proper symmetry of the generator. 

@@

    &\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}\nonumber
    \\&=\nonumber

@@

    \sum_{c=2}^{N}(E_{c1}^{x})\right)
    \alpha_{1}^{x}\sum_{b=2}^{N}\left(E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)+\sum_{a=2}^{N}\sum_{b=2}^{N}\alpha_{a}^{x}\left(E_{ba}^{x}+E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)
    \\&=\nonumber
    \sum_{a=2}^{N}\alpha_{a}^{x}E_{1a}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{b=2}^{N}E_{bb}^{x}=

@@

    \\&=\nonumber

@@

	\com{Double check this. Sum looks strange}

@@

        \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}\beta_{s_{3}}+\frac{(L+1-y_{1})}{(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}\beta_{s_{3}}

@@

        \frac{(L+1-y_{2})}{(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\beta_{s_{3}}+\frac{(L+1-y_{3})}{(L+1)}(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}\beta_{s_{2}}

@@

The third cumulant is given by 
	\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{3}}^{y_{3}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]
